Path2Vec: An NLP Based Mechanism for File Access Pattern Detection\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-09-10 master/paper.tex
paper

\section{Introduction}
Distributed file systems such as HDFS\cite{HDFS}, GlusterFS[], Ceph\cite{Ceph}, Lustre[] \textcolor{red}{etc}. have been widely deployed as back-end storage systems for parallel/distributed applications.
with the data scale continuously increased, i/o access latency between computing nodes and storage servers has become one of the severest bottlenecks in this big data era.
In order to narrow this performance gap, data caching/prefetching in file systems is one of the most well-known optimization techniques.
Caches(burst buffers?) with non-volatile memories(NVMs) and solid state drives(SSDs) are placed at different levels of the I/O stack to hide network and disk latency.

@@

\section{Related Work}
N-gram staging: high level works on data libraries
C-miner: low level on block-rate optimization.
meta data access optimizations.

@@

%\subsection{\textcolor{red}{edit}{Evaluation for dynamically file classification}}
\section{Conclusion}
In this paper, we systematically discuss the similarity between natural language processing and posix file systems,
and propose a new approch to represent posix file/direcory names with Skip-gram algorithm. 
With this embedding mechanism, we map the file/directory names into a high dimension vector space, 
where the relation between files can be dipicted by dot production of these two vectors.

>>>>

\section{Introduction}
Distributed file systems such as HDFS\cite{HDFS}, GlusterFS[], Ceph\cite{Ceph}, Lustre[] \textcolor{red}{etc}. have been widely deployed as back-end storage systems for parallel/distributed applications.
with the data scale continuously increased, I/O access latency between computing nodes and storage servers has become one of the severest bottlenecks in this big data era.
In order to narrow this performance gap, data caching/prefetching in file systems is one of the most well-known optimization techniques.
Caches(burst buffers?) with non-volatile memories(NVMs) and solid state drives(SSDs) are placed at different levels of the I/O stack to hide network and disk latency.

@@

\section{Related Work}
The I/O subsystem is becoming the bottleneck of high performance distributed systems, 
especially there are many communication intensive applications in them \cite{Related_Network_I/O_load_based}.
In order to achieve potential performance enhancements of storage systems, 
a variety of I/O history analysis-based I/O optimization mechanisms have been proposed previously 
\cite{Related_Multi_Layer_Event_Trace_Analysis} \cite{Related_Towards_an_I/O_tracing_framework_taxonomy} \cite{Related_DiskSeen} \cite{A_Prefetching_Scheme_Related} \cite{Scalable_IO_Tracing_Related}.
However, existing approaches including aforementioned ones have mostly focused on classifying I/O access patterns by analyzing either the history of applications’ I/O requests
\cite{Parallel_IO_Prefetching_Related} \cite{Learning_To_Classify_Related}
or the track of block access events \cite{Related_DiskSeen} \cite{A_Prefetching_Scheme_Related}, 
so that the analyzed results can be used for directing I/O optimization strategies, such as data prefetching.
The mechanism of data prefetching focuses on how to forecast future possible read requests, and thus, 
the accuracy of request prediction is critical to the effectiveness and applicability of data prefetching.

There is a wide range of sophisticated approaches to fulﬁll data prefetching, 
which utilize hidden Markov models, 
neural networks or other predictive algorithms to forecast I/O operations by analyzing I/O access patterns of the application 
\cite{Parallel_IO_Prefetching_Related} \cite{IO_Acceleration_with_Related} \cite{An_Automatic_Prefetching_Related} \cite{Reducing_File_System_Latency_Related} \cite{Automatic_ARIMA_Related}.
In summary, these mechanisms employ specific hard-coded algorithms to predict the application's future I/O access requests based on past I/O tracks for prefetching data.

@@

%\subsection{\textcolor{red}{edit}{Evaluation for dynamically file classification}}
\section{Conclusion}
In this paper, we systematically discuss the similarity between natural language processing and posix file systems,
and propose a new approach to represent posix file/direcory names with Skip-gram algorithm. 
With this embedding mechanism, we map the file/directory names into a high dimension vector space, 
where the relation between files can be dipicted by dot production of these two vectors.
